SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2018-12-03 results.tex
Results Section and PDF Images

@@

This section discusses the results obtained from running PPF, in
terms of cache Misses Per Kilo Instructions (MPKI) and Instruction Per
Cycle (IPC) metrics.  For SPEC 2017 suite, first we present the
results for single-threaded workloads then the results for multi-core
workloads are presented.

@@

As can be seen, PPF yields a speedup of \textbf{42.8\%} over
the baseline. This is equivalent to \textbf{7.8\%} over DA-AMPM, \textbf{9.7\%} over BOP
and \textbf{6.92\%} over SPP.  Out of the 95 simpoints developed for SPEC 2017, 
PPF nearly matches or outperforms most of the prefetchers on 91 simpoints.

Only in 607.cactuBSSN and 654.roms, PPF fails to match the improvement 
offered by BOP.

At its peak, PPF manages to get the IPC speedup of a factor of
over \textbf{3.39x} on the trace \textit{602.gcc\_s-2226B}.  This also
corresponds to speedup gain of \textbf{60\%} over the next best
prefetcher -- BOP. 
In general, benchmarks \textit{603.bwaves\_s, 605.mcf\_s, 623.xalancbmk\_s} 
and \textit{649.fotonik3d\_s} benefit the most from PPF, with the speedup over
SPP ranging from \textbf{10\% to 25\%}.

@@

<Discuss the extreme behaviour of \textit{623.xalancbmk\_s}:
Improvement over SPP is as high as 31\% and even reduces to -1.5\% on
traces of this benchmark>\newline

@@

<Discuss cases where coverage gets specially increased>
<Discuss accuracy on all traces>

\begin{figure}[h]
%%\includegraphics[width=\columnwidth]{4Core_SPEC2017}
\caption{Normalized speedup for 2 sets of 4-core workloads}
\label{Fig:4Core_SPEC2017}
\end{figure}

@@

\textit{4-core environment} Figure~\ref{Fig:4Core_SPEC2017} (a) 
shows a comparison of speedups
obtained on 4-core mix of memory intensive subset of SPEC 2017.  We
plot all the 4 prefetchers, normalized to baseline.  The workloads
have been sorted in the increasing order of IPC obtained with running PPF.
As can be seen,
PPF offers an IPC improvement by \textbf{51.7\%} on these traces.  This is
\textbf{XX\%} over the next best prefetcher -- \_\_; and \textbf{XX\%} 
and \textbf{YY\%} over \_\_ and \_\_ respectively.

@@

\begin{figure}[h]
\includegraphics[width=\columnwidth]{8Core_SPEC2017}
\caption{Normalized speedup for 2 sets of 8-core workloads}
\label{Fig:8Core_SPEC2017}
\end{figure}

@@

As can be seen, BOP offer a better improvement than 
SPP, for the memory intemsive mix, This can be attributed 
to BOP's inherent aggressive nature. DA-AMPM is also ahead of
SPP in both the mixes. Interestingly, in all these cases, 
PPF consistently outperforms the best performing prefetcher.

@@

@@

\textit{Low-Bandwidth DRAM}
Figure \_\_(a) shows the performance of PPF against other prefetchers. 
For sake of simplicity, we show 2 traces where PPF gives the most advantage
over baseline, 2 traces where PPF doesn't perform as well as the next
best prefetcher (replace with the prefetcher name once results are
available) and GeoMean across memory intensive and across all the 
SPEC 2017 traces. As can be seen, for the memory intensive subset,
 PPF improves baseline by XX\% and that is XX\% more than using SPP.

\textit{Small LLC}
Figure \_\_(b) shows the similar analysis of PPF.
For the memory intensive subset, a performance improvement of XX\% 
over baseline is seen with PPF, XX\% more than just SPP.

@@

@@

Fig~\ref{Fig:SPEC2006_1core} shows the speed-up achieved by BOP, SPP and PPF on
selected traces of SPEC 2006, along with the overall geometric mean
over whole of the benchmark and over memory-intensive subset of the
SPEC 2006 benchmark.  As can be seen, PPF provides a speed-up of
46.1\% over baseline, on the memory intensive subset of SPEC 2006
benchmark. This corresponds to \textbf{6.66\%} over SPP and {9.86\%} over BOP and DA-AMPM.  
On the whole of the SPEC 2006 suite, the speedup obtained is \textbf{22.4\%},
which is \text{3.34\%} ahead of SPP.

@@

As can be seen, the performance is very consistent given no prior
parameter tuning was done keeping SPEC 2006 in mind.  We attribute
this to the inherent adaptability of the perceptron model.  In
general, perceptron weights are able to adjust in real-time so as to
find the best possible correlation between the output and the given set of 
features.

>>>>

\begin{figure}[h]
\includegraphics[width=\columnwidth]{SPEC2017}
\caption{SPEC 2017 Single-Core IPC Speedup}
\label{Fig:SPEC2017_1core}
\end{figure}

@@

This section discusses the results obtained from running PPF, in
terms of prefetch cache coverage and Instruction Per
Cycle (IPC).  For SPEC 2017 suite, first we present the
results for single-threaded workloads then for multi-core
workloads.

@@

As can be seen, PPF yields a speedup of \textbf{42.8\%} over
the baseline. This is equivalent to \textbf{7.8\%} over DA-AMPM, \textbf{9.7\%} over BOP
and \textbf{6.92\%} over SPP.  Out of the 95 simpoints developed for SPEC 2017, 
PPF nearly matches or outperforms most of the prefetchers on 91 simpoints.
Only in 607.cactuBSSN and 654.roms, PPF fails to match the improvement 
offered by BOP.

At its peak, PPF manages to get the IPC speedup of a factor of
over \textbf{3.39x} on the trace \textit{602.gcc\_s-2226B}.  This also
corresponds to speedup gain of \textbf{60\%} over the next best
prefetcher -- BOP. 
In general, benchmarks \textit{bwaves, mcf, xalancbmk} 
and \textit{fotonik3d} benefit the most from PPF, with the speedup over
SPP ranging from \textbf{10\% to 25\%}.

@@

@@

\begin{figure}[h]
\includegraphics[width=\columnwidth]{4Core_SPEC2017}
\caption{Normalized speedup for 4-core workloads}
\label{Fig:4Core_SPEC2017}
\end{figure}

@@

\textit{4-core environment} Figure~\ref{Fig:4Core_SPEC2017} (a) 
shows a comparison of speedups
obtained on 4-core mix of memory intensive subset of SPEC 2017.  We
plot all the 4 prefetchers, normalized to the baseline.  The workloads
have been sorted in the increasing order of the speedup.
As can be seen,
PPF offers an IPC improvement by \textbf{51.7\%} on these traces.  
Compared to the base prefetcher -- SPP only, this is \textbf{11.9\%} more.
As compared to the next best prefetcher -- DA-AMPM, this is 
This is \textbf{10.2\%} and \textbf{17.4\%} over DA-AMPM, 
the next best prefetcher, and BOP, respectively.

@@

\begin{figure}[h]
\includegraphics[width=\columnwidth]{8Core_SPEC2017}
\caption{Normalized speedup for 8-core workloads}
\label{Fig:8Core_SPEC2017}
\end{figure}

@@

As can be seen, BOP offer a better improvement than 
SPP, for the memory intensive mix, This can be attributed 
to BOP's inherent aggressive nature. DA-AMPM is also ahead of
SPP in both the mixes. Interestingly, in all these cases, 
PPF consistently outperforms the best performing prefetcher.

@@

\begin{figure}[ht]
\includegraphics[width=\columnwidth]{AddnConstr}
\caption{IPC speedup for Small LLC and Low BW}
\label{Fig:AddnConstr}
\end{figure}

@@

Figure \ref{Fig:AddnConstr}(a) and (b) show the performance of PPF in a 
reduced LLC and low bandwidth constraints respectively. For the sake of brevity, 
we have only shownselected traces, followed
by the overall performance on the complete benchmark.
As can be seen, \textit{mcf} in low bandwidth conditions is prefetch averse.
In general, any prefetcher yields a negative speedup on that trace.
On \textit{roms} and \textit{cactuBSSN}, PPF is unable to match the performance 
achieved by the best prefetcher. On the other hand, PPF outperforms all the 
other prefetchers on \textit{xalancbmk} and \textit{imagick} benchmarks.
Overall, PPF gives a better improvement under small LLC condition and 
matches the best prefetcher -- BOP under low DRAM bandwidth condition.

@@

\begin{figure}[ht]
\includegraphics[width=\columnwidth,]{CloudSuite}
\caption{IPC Speedup for Multi-core CloudSuite Workloads}
\label{Fig:CloudSuite}
\end{figure}

@@

Fig~\ref{Fig:SPEC2006_1core} shows the speed-up achieved by BOP, SPP and PPF on
selected traces of SPEC 2006, along with the overall geometric mean
over whole of the benchmark and over memory-intensive subset of the
SPEC 2006 benchmark.  As can be seen, PPF provides a speed-up of
\textbf{46.1\%} over baseline, on the memory intensive subset of SPEC 2006
benchmark. This corresponds to \textbf{6.66\%} over SPP and \textbf{9.86\%} over BOP and DA-AMPM.  
On the whole of the SPEC 2006 suite, the speedup obtained is \textbf{22.4\%},
which is \textbf{3.34\%} ahead of SPP.

@@

Figure~\ref{Fig:CloudSuite} shows the performance benefit comparison of all 
the prefetch schemes on 4 different applications in the CloudSuite benchmark. 
In general, these applications are prefetch agnostic. Even in that scenario, 
PPF manages a \textbf{3.7\%} improvement over no prefetching, making it ahead of the 
next best prefetcher -- SPP, which provides a 3.08\% IPC speedup.

As can be seen, the performance is very consistent given no prior
parameter tuning was done keeping these benchmarks in mind.  We attribute
this to the inherent adaptability of the perceptron model.  In
general, perceptron weights are able to adjust in real-time so as to
find the best possible correlation between the output and the given set of 
features.
